Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2018-10-23 pkg/disttree/inst/draft/draft.Rnw
small corrections and change of order of subsections in the discussion
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2358 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: a3e7487d01efd56a103371034be8cf0acb55e46d

As mentioned before, distributional forests should not be seen as a replacement
for GAMLSS but rather as a complementary method. GAMLSS provide a powerful framework
in the field of distributional modeling as they allow for the combination of 
interpretability and a high goodnes-of-fit. For distributional forests, the focus
is mainly on forecasting skill, automatic variable selection and capturing also 
non-additive effects rather than on interpretability. Therefore, both approaches
provide valuable features and advantages that can complement each other in many 
applications as it can not be expected that one of them is in general better than 
the other. 
}

@@

\cite{Hastie+Tibshirani+Friedman:2001} and \cite{Breiman:2001} \hlc{recommend to 
build full-grown trees. Therefore, low values should be chosen for the stopping 
criteria} \code{minsplit}, \code{minbucket} and \code{alpha}.
\hlc{However, in a distributional model it also has to be considered that a 
minimal number of observations is required to allow for a reasonable 
estimation of parameters in each node. For that reason the minimal number
of observations for which statistical tests are performed in the 
distributional forest in} Section~\ref{sec:precipitation} is set to
50 (\code{minbucket}) \hlc{and the minimal number of observations on which
parameters are estimated is set to 20} (\code{minsplit}).

As stated by \cite{Breiman:2001} and \cite{Hastie+Tibshirani+Friedman:2001} 
\hlc{random forests do not overfit, not even for an increasing number of 
trees} (\code{ntree}). \hlc{Hence, it is recommended to build forests consisting 
of a large number of trees as this generally leads to an increase 
in accuracy. However, it also comes along with increasing computational costs. 
Therefore, ``a good choice results from a trade-off between computational 
complexity and accuracy''} (\cite{Biau+Scornet:2016}, p.~205).
\hlc{Following this advice we chose to build forests consisting of 100 trees.}

@@

\subsubsection{Distributional specifications}
%% choice of distribution mit Verweis auf Supplement distributions
\hlc{Choosing an adequate distributional family is a crucial step and forms
the basis required to build a well fitting model. Therefore, this
decision should be made thoughtfully. 
In the presented application we applied a Gaussian distribution left-censored 
at zero as this has proven to be a well working choice in
earlier literature} \citep{Stauffer+Mayr+Messner:2017}. 
\hlc{To test for robustness against distributional misspecifation 
different distributional assumptions have been considered as well. 
In Supplement 1 (Different Response Distributions) the exact
same evaluations as in} Section~\ref{sec:all} \hlc{are carried out for 15
observation stations, once employing a Gaussian hurdle model and once
with a logistic distribution left-censored at zero in order to account
for heavier tails. Under both assumptions the obtained results 
are similar to those presented in the paper applying a Gaussian distribution
left-censored at zero. In some settings the hurdle model leads to slight 
improvements, but this comes with more variability (especially for EMOS and the 
boosted GAMLSS). For the boosted GAMLSS the left-censored logistic distribution
shows slightly better results, however, only within a range of less than $2\%$
and not for all stations. Altogether, the distributional forest has proven to be 
very robust against distributional misspecifications.}

>>>>

As mentioned before, distributional forests should not be seen as a replacement
for GAMLSS but rather as a complementary method. GAMLSS provide a powerful framework
in the field of distributional modeling as they allow for the combination of 
interpretability and a high goodness-of-fit. For distributional forests, the focus
is mainly on forecasting skill, automatic variable selection and capturing also 
non-additive effects rather than on interpretability. Therefore, both approaches
provide valuable features and advantages that can complement each other in many 
applications as it can not be expected that one of them is in general better than 
the other. 
}

\subsubsection{Distributional specifications}
%% choice of distribution mit Verweis auf Supplement distributions
\hlc{Choosing an adequate distributional family is a crucial step and forms
the basis required to build a well fitting model. Therefore, this
decision should be made thoughtfully. 
In the presented application we applied a Gaussian distribution left-censored 
at zero as this has proven to be a well working choice in
earlier literature} \citep{Stauffer+Mayr+Messner:2017}. 
\hlc{To test for robustness against distributional misspecifation 
different distributional assumptions have been considered as well. 
In Supplement 1 (Different Response Distributions) the exact
same evaluations as in} Section~\ref{sec:all} \hlc{are carried out for 15
observation stations, once employing a Gaussian hurdle model and once
with a logistic distribution left-censored at zero in order to account
for heavier tails. Under both assumptions the obtained results 
are similar to those presented in the paper applying a Gaussian distribution
left-censored at zero. In some settings the hurdle model leads to slight 
improvements, but this comes with more variability (especially for EMOS and the 
boosted GAMLSS). For the boosted GAMLSS the left-censored logistic distribution
shows slightly better results regarding CRPS skill score, however, only within 
a range of less than $2\%$ and not for all stations. 
Altogether, the distributional forest has proven to be 
very robust against distributional misspecifications.}

@@

\cite{Hastie+Tibshirani+Friedman:2001} and \cite{Breiman:2001} \hlc{recommend to 
build full-grown trees. Therefore, low values should be chosen for the stopping 
criteria} \code{minsplit} and \code{minbucket} \hcl{together with a high significance 
level} \code{alpha}.
\hlc{However, in a distributional model it also has to be considered that a 
minimal number of observations is required to allow for a reasonable 
estimation of parameters in each node. For that reason, the minimal number
of observations for which statistical tests are performed in the 
distributional forest in} Section~\ref{sec:precipitation} is set to
50 (\code{minbucket}) \hlc{and the minimal number of observations on which
parameters are estimated is set to 20} (\code{minsplit}).

As stated by \cite{Breiman:2001} and \cite{Hastie+Tibshirani+Friedman:2001} 
\hlc{random forests do not overfit, not even for an increasing number of 
trees} (\code{ntree}). \hlc{Hence, it is recommended to build forests consisting 
of a large number of trees as this generally leads to an increase 
in accuracy. However, it also comes along with increasing computational costs. 
Therefore, ``a good choice results from a trade-off between computational 
complexity and accuracy''} (\cite{Biau+Scornet:2016}, p.~205).
\hlc{Following this advice we chose to build forests consisting of 100 trees which
is a commonly used value.}

@@
